The Effect of Oil Prices on Field Production: Evidence from the Norwegian Continental Shelf

### 2016-03-11 oil_prices_title.tex
final resubmission

\title{The Effect of Oil Price on Field Production: Evidence from the Norwegian Continental Shelf}
\author{Johannes Mauritzen\\
		Department of Economics\\
        BI Norwegian Business School\\
        Trondheim, Norway\\
        johannes.mauritzen@iot.ntnu.no\\
        \url{jmaurit.github.io}\\
		}
\date{\today}

@@

\begin{abstract}
I use detailed field-level data on Norwegian offshore oil production and a semi-parametric additive model to control for the production profile of fields to estimate the effect of oil prices on production.  I find no significant evidence of a concurrent reaction of field production to oil prices, though a slight lagged effect is found of the magnitude of approximately 2 to 5\% for a 10 dollar per barrel increase in the real price of oil.\\
\textbf{Keywords}: Oil production,Oil Prices, Norway, Generalized Additive Model.\\
\textbf{Words}: 5970
\end{abstract}

>>>>

\title{The Effect of Oil Prices on Field Production: Evidence from the Norwegian Continental Shelf}
\author{Johannes Mauritzen\\
        BI Norwegian Business School\\
        Department of Economics\\
        Trondheim Campus \\
        Trondheim, Norway\\
        johannes.mauritzen@bi.no\\
        \url{jmaurit.github.io}\\
		}
\date{\today}

@@

\begin{abstract}
I use detailed field-level data on Norwegian offshore oil production and a semi-parametric additive model to control for the production profile of fields to estimate the effect of oil prices on production. I find no significant evidence of a concurrent reaction of field production to oil prices, though a modest lagged effect is found of the magnitude of approximately 2\% to 7\% for a \$10 dollar per barrel increase in the real price of oil.\\
Keywords: Oil production, Oil Prices, Norway, Generalized Additive Model.
Words: 7100
\end{abstract}
